Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Finished Survey

The survey itself will be concise and straightforward, focusing on voting intentions, key issues, and demographic information. For data validation, in the survey, we will include attention-check questions as respondents are very likely to complete the form for an entry into a prize draw. We will also conduct multiple waves of the survey, we will adopt a "poll-of-polls" approach, aggregating responses from different waves while applying weights based on relevance.

@@

Ethically, our approach prioritizes respondent privacy and data security. We will ensure that participants’ responses remain anonymous and that all data is handled securely. Transparency is also essential; respondents will be informed about the survey’s sponsorship, methodology, and data use

@@

@@

## Survey Copy 
Welcome to our survey! We are conducting research to understand public perceptions and opinions related to the upcoming 2024 Presidential Election. Your responses are valuable in helping us gain insight into voter perspectives and preferences.

Contact Information: For any questions regarding this survey, please contact:

Name: [Jason Yang]
Email: ["jzc.yang@mail.utoronto.ca"]
Phone: ["123-234-5678"]

Your responses are confidential and will be used only for research purposes. This survey will take approximately [estimated time] to complete.

1. **Who do you intend to vote for in the 2024 U.S. Presidential Election?**
  - Kamala Harris (Democratic Party)
  - Donald Trump (Republican Party)
  - Undecided 
  - Other:

2. **How certain are you about your choice?  **
  - Very Certain
  - Somewhat certain
  - Unsure

3. **Which of the following issues are most important in deciding your vote? (Select up to 3)**
  - Economy and jobs
  - Healthcare
  - Climate Change
  - Education
  - Immigration
  - National Security 
  - Social justice and Equality 
  - Abortion rights
  - Gun control
  - Other:

4. **What is your age?**
  - 18-24
  - 24-34
  - 35-44
  - 45-54
  - 55-64
  - 65 or older

5. **What is your gender?**
  - Male 
  - Female
  - Non-binary/Other
  - Prefer not to say

6. **What is your race/ethnicity? (Select all that apply)**
  - White
  - Black or African American 
  - Hispanic or Latino 
  - Asian
  - Native American or Alaska Native
  - Native Hawaiian or Other Pacific Islander 
  - Other:

7. **In which U.S. state do you currently reside?**
  - ___

8. **If you voted in 2020, who did you vote for?**
  - Joe Biden 
  - Donald Trump 
  - Other:

>>>>

The survey itself will be concise and straightforward, focusing on voting intentions, key issues, and demographic information. For data validation, the survey will include attention-check questions as respondents are very likely to complete the form for an entry into a prize draw. We will also conduct multiple waves of the survey, we will adopt a "poll-of-polls" approach, aggregating responses from different waves while applying weights based on relevance.

@@

Ethically, our approach prioritizes respondent privacy and data security. We will ensure that participants’ responses remain anonymous and that all data is handled securely. Transparency is also essential; respondents will be informed about the survey’s sponsorship, methodology, and data use.

@@

### Budget Allocation

-

@@

## Survey Copy 
Welcome to our survey! We are conducting research to understand public perceptions and opinions related to the upcoming 2024 Presidential Election. Your responses are valuable in helping us gain insight into voter perspectives and preferences.
By participating, you will gain the chance to enter a prize draw. Prizes include a chance to win gift cards, exclusive merchandise, and special deals with our sponsors.

The survey should take about 10-15 minutes to complete.

Please note:

- Your Privacy are our top concern. All responses are confidential and will be used solely for research purposes. 
- Participation is entirely voluntary.

Contact Information

If you have any inquiries or need assistance with this survye, please contact us at:

- jzc.yang@mail.utoronto.ca
- 123-456-7891

1. **Are you eligible to vote in the upcoming 2024 U.S. Presidential Election?**
  - Yes 
  - No 
  - Not sure

2. **Who do you intend to vote for in the 2024 U.S. Presidential Election?**
  - Kamala Harris (Democratic Party)
  - Donald Trump (Republican Party)
  - Undecided 
  - Other:

3. **How certain are you about your choice?  **
  - Very Certain
  - Somewhat certain
  - Unsure

4. **Which of the following issues are most important in deciding your vote? (Select up to 3)**
  - Economy and jobs
  - Healthcare
  - Climate Change
  - Education
  - Immigration
  - National Security 
  - Social justice and Equality 
  - Abortion rights
  - Gun control
  - Other:

5. **What is your age?**
  - 18-24
  - 24-34
  - 35-44
  - 45-54
  - 55-64
  - 65 or older

6. **What is your gender?**
  - Male 
  - Female
  - Non-binary
  - Prefer not to say
  - Other:

7. **What is your race/ethnicity? (Select all that apply)**
  - White
  - Black or African American 
  - Hispanic or Latino 
  - Asian
  - Native American or Alaska Native
  - Native Hawaiian or Other Pacific Islander 
  - Other:

8. **In which U.S. state do you currently reside?**
  - [Drop Down With All the States]

9. **If you voted in 2020, who did you vote for?**
  - Joe Biden 
  - Donald Trump 
  - Other:

10. **Source of Information: What are your primary sources for political news?**
  - Television
  - Newspapers/Magazines
  - Online News Websites
  - Social Media
  - Radio 
  - Friends and Family 
  - Other (Please specify): _____

11. **What is your highest level of education?**
  - High school graduate, equivalent, or less
  - College Degree
  - Associate degree
  - Bachelor's degree
  - Graduate degree

12. **Would you be willing to participate in follow-up surveys regarding the election?** 
  - Yes
  - No

13. **Do you have any additional comments or concerns about the 2024 election?**
  - [Open Text Response]
